Adaptive group-regularized logistic elastic net regression Supplementary material

### 2019-02-20 docs/supplement.Rnw
added barplots of multiplier estimates to metabolomics_alzheimer.R example

\documentclass[a4paper,hidelinks]{article}
\usepackage{bm,amsmath,amssymb,amsthm,amsfonts,graphics,graphicx,epsfig,rotating,caption,subcaption,natbib,appendix,titlesec,multicol,hyperref,verbatim,bbm,algorithm,algpseudocode,pgfplotstable,threeparttable, booktabs,mathtools,dsfont,parskip}

@@

% load packages and set options
<<settings, include=FALSE, echo=FALSE>>=
library(cambridge)
opts_knit$set(base.dir="../figs")
opts_chunk$set(fig.align='center', echo=FALSE, fig.path="../figs/", cache=FALSE,
               message=FALSE)
@

% read figure code
<<figures, include=FALSE>>=
read_chunk("../code/figures.R")
@

@@

\subsection{Expectation and variance}
The expectation and variance of $\beta$ are:
\begin{align*}
\E[\beta] &= g(\lambda_1,\lambda_2) \int_{-\infty}^{\infty} \beta \cdot \exp\[-\frac{1}{2} (\lambda_1 |\beta| + \lambda_2 \beta^2)\] d\beta=0, \\
\V[\beta] &= g(\lambda_1,\lambda_2) \int_{-\infty}^{\infty} \beta^2 \cdot \exp\[-\frac{1}{2} (\lambda_1 |\beta| + \lambda_2 \beta^2)\] d\beta - \E[\beta]^2\\ &= \frac{\lambda_1^2}{4 \lambda_2^2} + \frac{1}{\lambda_2} - \frac{\lambda_1}{2 \lambda_2^{3/2}} \phi \( \frac{\lambda_1}{2 \sqrt{\lambda_2}} \) \Phi \(\frac{-\lambda_1}{2 \sqrt{\lambda_2}} \)^{-1}.
\end{align*}

@@

>>>>

% set options
<<settings, include=FALSE, echo=FALSE>>=
opts_knit$set(root.dir="..", base.dir="../figs")
opts_chunk$set(fig.align='center', fig.path="../figs/", 
               echo=FALSE, cache=FALSE, message=FALSE)
@

% read figure code
<<figures, include=FALSE>>=
read_chunk("code/figures.R")
@

\documentclass[a4paper,hidelinks]{article}
\usepackage{bm,amsmath,amssymb,amsthm,amsfonts,graphics,graphicx,epsfig,
rotating,caption,subcaption,natbib,appendix,titlesec,multicol,hyperref,verbatim,
bbm,algorithm,algpseudocode,pgfplotstable,threeparttable,booktabs,mathtools,
dsfont,parskip}

@@

@@

  \subsection{Expectation and variance}
  The expectation and variance of $\beta$ are:
  \begin{align*}
  \E[\beta] &= g(\lambda_1,\lambda_2) \int_{-\infty}^{\infty} \beta \cdot \exp\
  -\frac{1}{2} (\lambda_1 |\beta| + \lambda_2 \beta^2)\] d\beta=0, \\
  \V[\beta] &= g(\lambda_1,\lambda_2) \int_{-\infty}^{\infty} \beta^2 \cdot
  \exp\[-\frac{1}{2} (\lambda_1 |\beta| + \lambda_2 \beta^2)\] d\beta -
  \E[\beta]^2\\ &= \frac{\lambda_1^2}{4 \lambda_2^2} + \frac{1}{\lambda_2} -
  \frac{\lambda_1}{2 \lambda_2^{3/2}} \phi \( \frac{\lambda_1}{2 
  \sqrt{\lambda_2}} \) \Phi \(\frac{-\lambda_1}{2 \sqrt{\lambda_2}} \)^{-1}.
  \end{align*}

@@

\section*{Session info}
<<r session-info, eval=TRUE, echo=TRUE, tidy=TRUE>>=
devtools::session_info()
@
